### 2014-11-02 evaluation.tex
edits

Figure~\ref{grf:BA-lat} and~\ref{grf:BA-tp} analyzes the latency and throughput
of operations in bank account example as we increase the number of clients. The
benchmark uniformly chose from 100,000 keys, where the operation spread was
25\% withdraw, 25\% deposit and 50\% getBalance. Here, the lines marked EC and
CC correspond to all operations being assigned EC and CC consistency levels.
These levels compromise correctness as withdraw has to be and SC operation. The
line SC corresponds to a configuration where all operations are strongly
consistent; this ensures application correctness. \name corresponds to our
implementation, which classifies operations based on their contracts. At 512
clients, \name implementation was within 30\% of latency and 12\% of throughput
of EC, while providing correctness, whereas SC operations had 162\% higher
latency and 52\% lower throughput than EC operations. This illustrates the
benefit of fine-grained contract classification in \name.

>>>>

Figure~\ref{grf:BA-lat} and~\ref{grf:BA-tp} analyzes the latency and throughput
of operations in bank account example as we increase the number of clients in
\cf{1DC} configuration. The benchmark uniformly chose from 100,000 keys, where
the operation spread was 25\% withdraw, 25\% deposit and 50\% getBalance. Here,
the lines marked EC and CC correspond to all operations being assigned EC and
CC consistency levels. These levels compromise correctness as withdraw has to
be and SC operation. The line SC corresponds to a configuration where all
operations are strongly consistent; this ensures application correctness. \name
corresponds to our implementation, which classifies operations based on their
contracts. At 512 clients, \name implementation was within 30\% of latency and
12\% of throughput of EC, while providing correctness, whereas SC operations
had 162\% higher latency and 52\% lower throughput than EC operations. This
illustrates the benefit of fine-grained contract classification in \name.
